\documentclass[margin,line]{res}
\oddsidemargin -.5in
\evensidemargin -.5in
\itemsep=0in
\parsep=0in
\topmargin -0.4in
\leftmargin 0.4in
\textheight=10.0in
\newsectionwidth{1.1in}
\textwidth=6.3in
%\setlength{\parskip}{-0.1mm plus 3mm minus 3mm}

\newenvironment{list1}{
%\begin{list}{$\ast$}{%
  \begin{list}{$\bowtie$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0.05in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{-0.1in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{times}
\usepackage{textcomp}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\begin{document}

\name{ \Large Harshal Patil }
\address{  	New York, NY $\bullet$ 917-558-4825 $\bullet$ 
		\href{mailto: harsshal@nyu.edu} {harsshal@nyu.edu} $\bullet$
          	\href{https://sites.google.com/site/harsshal/}{https://sites.google.com/site/harsshal/} }

\vspace {0.1in}
\begin{resume}
\section{\sc Highlights}
\begin{list2}
\begin{minipage}{0.5\linewidth}
\item Hands-on Market Structure Experience.
\item Strong technical background.
\end{minipage}
\begin{minipage}{0.4\linewidth}
\item Performance under pressure.
\item Solid mathematical base.
\end{minipage}
\end{list2}

\section{\sc Professional Experience}
{\bf WorldQuant LLC / Millennium Partners} \hfill {\bf 2010 - Present}\\
{\bf Quant Macro PM Assistant / Researcher} \hfill {\bf 2018 - Present}\_
\begin{list2}
\item Wrote {\bf C/C++} trading system API to connect to Central WQ trading system for faster executions.
\item Setup data infrastructure in {\bf Python} using MariaDB for easier cleaning and modeling of data.
\item Optimized portfolio of signals based on constraints to achieve low risk / high Sharpe portfolios.
\end{list2}

{\bf Vice President, Trading} \hfill {\bf 2015 - 2018}\_
\begin{list2}
\item Researched new lit and dark venues, new markets to improve liquidity profile.
\item Monitored Fill-rates, {\bf TCA} for over 2500 portfolios to achieve fill-rate of 99\% for TOP4000 universe in US.
\item Improved slippage to VWAP to 6 bps from 10 bps by ironing out anomalies in executions.
\item Provided insights to PMs from biggest winners / losers, changing market structure by writing digests.
\item Designed complete end-to-end alternative execution system to avoid conflict between investors for {\bf JV fund Launch} including selection of prime brokers, accounts, instrument selection for capital transition.
\end{list2}

{\bf Vice President, Operations} \hfill {\bf 2012 - 2015}\_
\begin{list2}
\item Performed SOD and EOD procedures like CACS / PNL , to make sure smooth trading for the firm.
\item Designed and Implemented FX trading system for complete electronic trading of FX Spots and Forwards.
\item Collaborated with Portfolio Managers and Developers for improving efficiency of the development cycle.
\item Worked with developers to accommodate changes in Market structure and Regulations.
\end{list2}

{\bf Trading System Operator} \hfill {\bf 2010 - 2012}\_
\begin{list2}
\item Supported over 40 Portfolio Managers and around 1000 portfolios.
\item Developed various features in trading system, reports, monitoring tools.
\end{list2}


\vspace {0.1in}
{\bf NYU Stern Research Computing} \hfill {\bf 2008 - 2010}\\
On-campus Research Assistant (Platform - {\bf Linux}, Languages - {\bf C/C++}, Perl, Shell)
\begin{list2}
\item Helped Professors with research projects like \href{https://vlab.stern.nyu.edu/doc?topic=vlab}{https://vlab.stern.nyu.edu/doc?topic=vlab}.
\item Implemented an IP randomizer; Perl Visualization tools.
\end{list2}

{\bf Persistent Systems} ({\em Software Engineer}) \hfill {\bf 2007 - 2008}\\
Virtual iSCSI Tape (Platform - {\bf Linux Kernel 2.6.25}, Languages - {\bf C/C++})
\begin{list2}
\item Modified kernel module and user mode component of iSCSI target utility (iSCSI client) to provide
tape impersonation of SCSI disks over iSCSI network by hacking into SCSI stream commands and responses.
\end{list2}

{\bf Calsoft Systems Limited} ({\em Undergraduate Intern}) \hfill {\bf 2006 - 2007}\\
Zipped RAM Pages (Platform - {\bf Linux Kernel 2.6.19}, Languages - {\bf C/C++})
\begin{list2}
\item Inserted a new level into the memory hierarchy, where a portion of main memory is allocated for the Zipped cache. This portion is used to store more pages zipped by data compression algorithm to reduce page faults.
\end{list2}


\section{\sc Education}
{\bf WorldQuant University} ({\em Accredited University offering 2-year Masters}) \hfill {\bf  2015 - 2017}\\
Master of Science, Quantitative Finance {\em (One of the 6 students who graduated in first batch, out of 150 students)}

{\bf New York University}, Courant Institute of Mathematical sciences, New York, NY \hfill {\bf 2008 - 2010}\\
Master of Science, Computer Science

{\bf Pune University}, Rajarshi Shahu College of Engineering, Pune, Maharashtra, India \hfill{\bf 2003 - 2007}\\
Bachelor of Engineering, Computer Science


\section{\sc Achievements \& Honors}
\begin{list2}
\item Secured 16th position in {\bf Mathematical Olympiad} held across the States of Maharashtra and Goa.
\item Won various {\bf C Programming Competitions} and {\bf Chess Competitions} held across State of Maharashtra.
\end{list2}


\end{resume}
\end{document}
